Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2021-02-06 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny

mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein),

@@

Vesicles 
%(self-enclosed lipid bilayer membranes) 
have been used as a
model system to study reshaping, remodeling, and scission of cell
membranes due to osmotic stress~\cite{OgleckaEtAl2014_eLife, BhatiaRobinsonDimova2020_SoftMatt,
CamposSaric2020_bioRxiv, Dimova2020_GVB, BhatiaChrist2020_SoftMatt}.
%Under an osmotic shock, a vesicle may undergo oscillatory variation in
%its enclosed volume~\cite{ChabanonHoLiedberg2017_BJ}. 
%When trapped in a
%microfluidic channel, an osmotic shock induces vesicle shape changes,
%tank-treading and tumbling
%motions~\cite{BhatiaRobinsonDimova2020_SoftMatt,
%BhatiaChrist2020_SoftMatt}, an 
These results illustrate that the permeating water
flow is inevitably coupled with the mechanical pressure jump across the
membrane~\cite{yao-mor2017}, which could become comparable to osmotic
stress when the membrane deformation is large~\cite{LiMoriSun2015_PRL,
yao-mor2017}. 
%
In microfluidic experiments, it is challenging to keep a freely
suspended red blood cell or vesicle in a steady flow for more than a few
hours. It is also difficult to quantify the vesicle surface-to-volume
ratio accurately~\cite{MinetttiCallensCoupier2008_AppliedOptics}. Using
numerical simulations we can quantify the effects of water permeability
on the hydrodynamics of a vesicle under mechanical stresses.  Without an
osmotic gradient, we first show that a freely suspended semipermeable
vesicle behaves differently from an impermeable vesicle over a long
time. Next we show that
%, at normal physiological conditions,
the permeating water flow can be amplified by extreme confinement to give rise to observable change in both hydrodynamics and water content. 
These results provide insight into quantifying the effects of membrane permeability on vesicle hydrodynamics in microfluidics.
%
%shed light on the dynamic aging process of
%living cells that constantly go through flows and constrictions over a
%period of days.

@@

\section{Formulation\label{sec:formulation}}
We consider a two-dimensional semipermeable vesicle (permeable only to
water) suspended in a viscous fluid (Figure~\ref{fig:sketch}), and we
let $\gamma$ denote the membrane boundary. We let
$\alpha=4\pi A/L^2$ be the vesicle's reduced area where $A$ is its area
and $L$ is its length. To focus on the effect of water flow on vesicle
hydrodynamics in various conditions, we assume the fluid is the same
inside and outside the vesicle membrane. On the membrane the permeable
water flux gives rise to a difference between the fluid velocity
${\uu}({\xx}\in \gamma)$ and the membrane velocity
$\dot{\xx}$~\cite{yao-mor2017}:
\begin{align}
\label{eq:water_flux}
  \uu - \dot{\xx} = - k_w (R T \triangle c + \ff_\mathrm{mem} \cdot \nn) \nn, \qquad
  \xx \in \gamma,
\end{align}
where $\nn$ is the outward normal (Figure~\ref{fig:sketch}), $k_w$ is
the hydraulic conductivity (m$^2$s/kg), $R$ is the ideal gas constant,
$T$ is the temperature (K), $\triangle c$ is contrast in a solute
concentration (mol/volume), and $\ff_\mathrm{mem}$ is the membrane
stress that consists of both bending $ \ff_\mathrm{ben}= -k_b
\xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$, where $s$
is the arclength, $\sigma = \Lambda - \frac{3}{2}\kappa^2$, $\Lambda$ is the
membrane tension, and $\kappa$ is the membrane curvature.

Using $k_w\sim 10^{-12}$ m$^2$s/kg 
%(typical of mammalian cell membranes~\cite{LiMoriSun2015_PRL}) 
and an osmolarity $\triangle c = 0.1$ mol/L (consistent with the osmotic
filtration experiments~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the
corresponding water flow is of the order $v_\mathrm{o}=0.1 \; \mu$m/s.
Assuming a membrane bending stiffness of $k_b = 10^{-19}$ J, a membrane
tension of $10^{-3}$ N/m (one tenth of the lysis tension), and a
characteristic length scale of $10^{-6}$ m, the tension contribution
($v_\mathrm{t}$) and elastic stress contribution ($v_\mathrm{e}$) to the
permeable water flow can be scaled to $v_\mathrm{o}$ as
$v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=10^{0}:10^{-2}:10^{-6}$.
Furthermore, we note that in the absence of an osmotic stress
($\triangle c = 0$), the permeating water flow may be non-negligible
when the membrane tension becomes large due to the external stress such
as the hydrodynamic stress from an external flow or confinement. In the
following we explore both.

In this work we focus on the mechanical component of the water flux
in~\eqref{eq:water_flux} with $\triangle c =0$. In our
non-dimensionalization the hydraulic conductivity is scaled to $R_0/\mu$
(where $R_0$ is a characteristic length and $\mu$ is the solvent
viscosity): $\beta = k_w/(R_0/\mu)$,
$\beta=0$ for an impermeable vesicle, and $\beta>0$ for a semipermeable
vesicle. Under strong confinement, a large value of $\beta$ is needed in
our simulations to keep the membrane tension below the threshold value
for membrane poration $\sim 10^{-3}$ N/m. Such large value of $\beta$
may pertain to red blood cell membranes with aquaporin proteins.

In our formulation, an inextensible semipermeable vesicle is suspended in a viscous Newtonian fluid 
(in domain $\Omega$).  The vesicle membrane $\gamma$ is parameterized as $\xx(s,t)$
where $s$ is arclength and $t$ is time. In the suspending fluid the flow
velocity $\uu$ and pressure $p$ are governed by the incompressible 
Stokes equations
\begin{align}
  \label{eqn:governing}
  -\nabla p + \mu \triangle \uu = 0, \quad
  \nabla \cdot \uu = 0, \qquad \xx \in \Omega \setminus \gamma,
\end{align}
where $\mu$ is the fluid viscosity. When $\Omega$ is an unconfined
geometry, the condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ as $|\xx|
\rightarrow \infty$ is enforced.

We non-dimensionalize the governing equations by a
characteristic length scale $R_0 = 10^{-6}$ m, a bending stiffness $k_b
= 10^{-19}$ J, and fluid viscosity $5 \times 10^{-2}$ kg/ms. We scale
time by $\tau = \mu R_0^3/k_b = 0.5\;s$, the velocity by $R_0/\tau =
2\;\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$ Pa, the tension by
$k_b/R_0^2 = 10^{-7}$ N/m, and the permeability by $R_0/\mu = 10^{-3}$
m$^2$s/kg. Under this nondimensionalization, a two-dimensional
semipermeable vesicle in a viscous fluid is characterized by (a) its
reduced area $\alpha = 4\pi A/L^2 \in (0,1]$, where $L$ is the vesicle
length and $A$ is its area, and (b) its permeability $\beta = k_w \mu
/R_0$. In two dimensions, the membrane length is conserved by the local
inextensibility condition, but the enclosed area is not conserved
because of semipermeability. Therefore, the reduced area is dynamic. We
convert the apparent permeability of a polyunsaturated PC
bilayer~\cite{OlbrichRawiczNeedhamEtAl2000_BJ} to the hydraulic
conductivity $k_w$ using the conversion
in~\cite{FettiplaceHaydon1980_PhysRev}, and found that $10^{-14}\le
k_w\le 10^{-12}$ m$^2$s/kg, thus $\beta$ is in the range $10^{-11}\le
\beta\le 10^{-9}$.

In the confined examples, we enforce a
no-slip boundary condition along the top and bottom of the channel and a
Hagen–Poiseuille flow at the inlet and outlet---this boundary condition
has been used in similar vesicle setups~\cite{qua-bir2014,
rah-vee-bir2010, lu-rah-zor2017}. Along the vesicle membrane $\gamma$,
mass continuity, force balance, and local inextensibility are enforced
by requiring
\begin{align}
  \label{eqn:jump}
  \jump{\uu} = 0, \quad
  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad
  \xx_s \cdot \uu_s = 0,
\end{align}
where $\nn$ is the outward normal of $\gamma$, $\jump{\cdot}$ is the
jump across the interface, and $T$ is the hydrodynamic stress tensor.
The membrane force $\ff_\mathrm{mem}$ is the sum of a bending force
with bending modulus $k_b$ and a force due to the tension $\Lambda$.
Following~\cite{vee-gue-zor-bir2009}, we introduce the variable $\sigma
= \Lambda - \frac{3}{2}\kappa^2$, where $\kappa$ is the vesicle curvature. Then,
the bending and tension forces corresponding to the Helfrich energy are
$\ff_\mathrm{ben} = -k_b \xx_{ssss}$ and $\ff_\mathrm{ten} = (\sigma
\xx_s)_s$.

Semipermeability is introduced by modifying the vesicle velocity from
the standard no-slip condition $\dot{\xx} = \uu(\xx)$. Instead,
the permeating water flux through the lipid bilayer membrane is proportional to the
membrane traction~\cite{yao-mor2017}. That is, 
\begin{align}
  \label{eqn:vesicleFlux}
  \uu - \dot{\xx} = - \beta (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
  \xx \in \gamma,
\end{align}
where $\beta = k_w/(R_0/\mu)$ is the dimensionless membrane permeability for water.

@@

Since the fluid satisfies the Stokes equations, the velocity and
pressure can be represented as layer potentials. Given the interfacial
boundary conditions~\eqref{eqn:jump}, the fluid velocity is
\begin{align}
  \uu(\xx) = \uu_\infty(\xx) + \SS[\ff_\mathrm{mem}](\xx), \quad
    \xx \in \Omega,
\end{align}
where $\SS$ is the single-layer potential
\begin{align}
  \SS[\ff](\xx) = \frac{1}{4\pi} \int_{\gamma} \left(
    -\mathbf{I} \log\rho + \frac{\rr \otimes \rr}{\rho^2} \right)
    \ff(\yy) ds_{\yy},
%  \SS[\ff](\xx) = \frac{1}{4\pi\mu} \int_{\gamma} \left(
%    -\mathbf{I} \log\rho + \frac{\rr \otimes \rr}{\rho^2} \right)
%    \ff(\yy) ds_{\yy},
\end{align}
with $\rr = \xx - \yy$ and $\rho = |\rr|$. Imposing the flux
condition~\eqref{eqn:vesicleFlux} and the inextensibility condition, the
vesicle velocity satisfies the boundary integral equation
\begin{align}
  \label{eqn:vesVelocity}
  \dot{\xx} &= \uu_\infty(\xx) + \beta (\ff_\mathrm{mem}\cdot\nn)\nn
  + \SS [\ff_\mathrm{mem}](\xx),  \quad
  \xx_s \cdot \dot{\xx}_s = 0.
\end{align}
In confined geometries, the far field term $\uu_\infty(\xx)$ is replaced
by a double-layer potential with an unknown density defined on
$\partial\Omega$. The density function is used to satisfy the boundary
condition on $\partial\Omega$.

@@

\section{Hydrodynamics of a semipermeable vesicle in free space}
To highlight the effects of membrane permeability to water, we consider
a single semipermeable vesicle, with (dimensionless) permeability
coefficient $\beta>0$, in familiar configurations: In free space we
place a semipermeable vesicle in a quiescent flow, a planar shear flow,
and a Poiseuille flow. For each example, we fix the vesicle length and
examine the enclosed water content as a dynamic consequence of water
flow, vesicle shape deformation, and membrane tension distribution.
%
Under these flows, our simulations show
that the steady state of an impermeable vesicle is different from that of a semipermeable vesicle, which depends only on the strength of the external flow and is insensitive to permeability $\beta$ (as long as $\beta>0$). We find that  the time in the dynamic evolution towards equilibrium is scaled by $\beta^{-1}$: the smaller $\beta$ is the longer it takes to reach the steady state.

@@

\section{A semipermeable vesicle under strong confinement}
Here we consider a semipermeable vesicle under strong confinement: a
long closely-fit channel and a contracting channel. In a narrow
microfluidic channel, a large pressure jump is often needed to push the
vesicle through a closely-fit channel~\cite{abk-fai-sto2006}.  Our
simulations show that such a configuration can lead to an amplification
of water permeation at a time scale shorter than a few minutes. In
addition, we find that a large value of $\beta$ is needed to keep the
membrane tension below the threshold value for membrane poration. Such
high permeability for water may be regarded as an indication that the
lipid bilayer membrane is porated under strong confinement, and our
model vesicle is for a porated vesicle within the Helfrich free energy
framework.  As in the previous examples, we fix the vesicle length and
examine the enclosed water content as a dynamic consequence of water
flow, vesicle shape deformation, and membrane tension distribution.

@@

\acknowledgments
We thank Howard Stone, Michael J.~Shelley, Petia Vlahovska,
Chaoqui Misbah, Manouk Abkarian, Sangwoo Shin, and Shravan
K.~Veerapaneni for discussions. B.Q.~acknowledges support from the
Simons Foundation, Mathematics and Physical Sciences-Collaboration
Grants for Mathematicians, Award Number 527139.  Y.-N.Y.~acknowledges
support from NSF (DMS 1614863, DMS 195160) and Flatiron Institute, part
of Simons Foundation.

>>>>

mN/m (see \citet{RazizadehNikfarPaulLiu2020_BJ} and references therein),

@@

Vesicles 
%(self-enclosed lipid bilayer membranes) 
have been used as a
model system to study reshaping, remodeling, and scission of cell
membranes due to osmotic stress~\cite{OgleckaEtAl2014_eLife, BhatiaRobinsonDimova2020_SoftMatt,
CamposSaric2020_bioRxiv, Dimova2020_GVB, BhatiaChrist2020_SoftMatt}.
%Under an osmotic shock, a vesicle may undergo oscillatory variation in
%its enclosed volume~\cite{ChabanonHoLiedberg2017_BJ}. 
%When trapped in a
%microfluidic channel, an osmotic shock induces vesicle shape changes,
%tank-treading and tumbling
%motions~\cite{BhatiaRobinsonDimova2020_SoftMatt,
%BhatiaChrist2020_SoftMatt}, an 
These results illustrate that the permeating water
flow is inevitably coupled with the mechanical pressure jump across the
membrane~\cite{yao-mor2017}, which could become comparable to osmotic
stress when the membrane deformation is large~\cite{LiMoriSun2015_PRL,
yao-mor2017}. 
%
In microfluidic experiments, it is challenging to keep a freely
suspended red blood cell or vesicle in a steady flow for more than a few
hours. It is also difficult to quantify the vesicle surface-to-volume
ratio accurately~\cite{MinetttiCallensCoupier2008_AppliedOptics}. Using
numerical simulations we can quantify the effects of water permeability
on the hydrodynamics of a vesicle under mechanical stresses.  Without an
osmotic gradient, we first show that a freely suspended semipermeable
vesicle behaves differently from an impermeable vesicle over a long
time in \S~\ref{sec:free_space}. Next in \S~\ref{sec:confinement} we show that
%, at normal physiological conditions,
the permeating water flow can be amplified by extreme confinement to give rise to observable change in both  vesicle hydrodynamics and vesicle's water content. 
These results provide insight into quantifying the effects of membrane permeability on vesicle hydrodynamics in microfluidics.
%
%shed light on the dynamic aging process of
%living cells that constantly go through flows and constrictions over a
%period of days.

@@

\section{Formulation\label{sec:formulation}}
We consider a two-dimensional semipermeable vesicle (permeable only to
water) suspended in a viscous fluid (Figure~\ref{fig:sketch}), and we
let $\gamma$ denote the membrane boundary, of length $L$ and enclosing an area $A$.
%
%$\alpha=4\pi A/L^2$ be the vesicle's reduced area where $A$ is its area
%and $L$ is its length. 
%
To focus on the effect of water flow on vesicle
hydrodynamics in various conditions, we assume the fluid is the same
inside and outside the vesicle membrane. On the membrane the permeable
water flux gives rise to a difference between the fluid velocity
${\uu}({\xx}\in \gamma)$ and the membrane velocity
$\dot{\xx}$~\cite{yao-mor2017}:
\begin{align}
\label{eqn:water_flux}
  \uu - \dot{\xx} = - k_w (R T \triangle c + \ff_\mathrm{mem} \cdot \nn) \nn, \qquad
  \xx \in \gamma,
\end{align}
where $\nn$ is the outward normal (Figure~\ref{fig:sketch}), $k_w$ is
the hydraulic conductivity (m$^2$s/kg), $R$ is the ideal gas constant,
$T$ is the temperature (K), $\triangle c$ is contrast in a solute
concentration (mol/volume), and $\ff_\mathrm{mem}$ is the membrane
stress that consists of both bending $ \ff_\mathrm{ben}= -k_b
\xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$, where $s$
is the arclength, $\sigma = \Lambda - \frac{3}{2}\kappa^2$, $\Lambda$ is the
membrane tension, and $\kappa$ is the membrane curvature.

Using $k_w\sim 10^{-12}$ m$^2$s/kg 
%(typical of mammalian cell membranes~\cite{LiMoriSun2015_PRL}) 
and an osmolarity $\triangle c = 0.1$ mol/L (consistent with the osmotic
filtration experiments~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the
corresponding water flow is of the order $v_\mathrm{o}=0.1 \; \mu$m/s.
Assuming a membrane bending stiffness of $k_b = 10^{-19}$ J, a membrane
tension of $10^{-3}$ N/m (one tenth of the lysis tension), and a
characteristic length scale of $10^{-6}$ m, the tension contribution
($v_\mathrm{t}$) and elastic stress contribution ($v_\mathrm{e}$) to the
permeable water flow can be scaled to $v_\mathrm{o}$ as
$v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=10^{0}:10^{-2}:10^{-6}$.
Furthermore, we note that in the absence of an osmotic stress
($\triangle c = 0$), the permeating water flow may be non-negligible
when the membrane tension becomes large due to the external stress such
as the hydrodynamic stress from an external flow or confinement. 
In this work we set $\triangle c =0$ in Equation~\eqref{eqn:water_flux}  to
focus on the water flux driven by the pressure difference due to an external flow or confinement.

%In our non-dimensionalization the hydraulic conductivity is scaled to $R_0/\mu$
%(where $R_0$ is a characteristic length and $\mu$ is the solvent
%viscosity): $\beta = k_w/(R_0/\mu)$,
%$\beta=0$ for an impermeable vesicle, and $\beta>0$ for a semipermeable
%vesicle. Under strong confinement, a large value of $\beta$ is needed in
%our simulations to keep the membrane tension below the threshold value
%for membrane poration $\sim 10^{-3}$ N/m. Such large value of $\beta$
%may pertain to red blood cell membranes with aquaporin proteins.

In our formulation, a semipermeable vesicle is suspended in a viscous Newtonian fluid 
(in domain $\Omega$).  The vesicle membrane $\gamma$ is parameterized as $\xx(s,t)$
where $s$ is arclength and $t$ is time. In the suspending fluid the flow
velocity $\uu$ and pressure $p$ are governed by the incompressible 
Stokes equations
\begin{align}
  \label{eqn:governing}
  -\nabla p + \mu \triangle \uu = 0, \quad
  \nabla \cdot \uu = 0, \qquad \xx \in \Omega \setminus \gamma,
\end{align}
where $\mu$ is the fluid viscosity. When $\Omega$ is an unconfined
geometry, the condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ as $|\xx|
\rightarrow \infty$ is enforced. 
%
Along the vesicle membrane $\gamma$,
mass continuity, force balance, and local inextensibility are enforced
by requiring
\begin{align}
  \label{eqn:jump}
  \jump{\uu} = 0, \quad
  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad
  \xx_s \cdot \uu_s = 0,
\end{align}
where $\nn$ is the outward normal of $\gamma$, $\jump{\cdot}$ is the
jump across the interface, and $T$ is the hydrodynamic stress tensor.
The membrane force $\ff_\mathrm{mem}$ is the sum of a bending force
with bending modulus $k_b$ and a force due to the tension $\Lambda$.
Following~\cite{vee-gue-zor-bir2009}, we introduce the variable $\sigma
= \Lambda - \frac{3}{2}\kappa^2$, where $\kappa$ is the vesicle curvature. Then,
the bending and tension forces corresponding to the Helfrich energy are
$\ff_\mathrm{ben} = -k_b \xx_{ssss}$ and $\ff_\mathrm{ten} = (\sigma
\xx_s)_s$.

We non-dimensionalize the governing equations (Equations~(\ref{eqn:water_flux}-\ref{eqn:jump})) by a
characteristic length scale $R_0 = 10^{-6}$ m, a bending stiffness $k_b
= 10^{-19}$ J, and fluid viscosity $5 \times 10^{-2}$ kg/ms. We scale
time by $\tau = \mu R_0^3/k_b = 0.5\;s$, the velocity by $R_0/\tau =
2\;\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$ Pa, the tension by
$k_b/R_0^2 = 10^{-7}$ N/m, and the permeability by $R_0/\mu = 10^{-3}$
m$^2$s/kg. Under this nondimensionalization, a two-dimensional
semipermeable vesicle in a viscous fluid is characterized by (a) its
reduced area $\alpha = 4\pi A/L^2 \in (0,1]$, where $L$ is the vesicle
length and $A$ is its area, and (b) its permeability $\beta = k_w \mu
/R_0$. 
In two dimensions, the conservation of total lipids in the membrane corresponds to the inextensibility (fixed length $L$) of $\gamma$.
Due to semipermeability to water ($\beta>0$),  the enclosed area $A$ is not conserved and the reduced area $\alpha$ is dynamic.

@@

Since the fluid satisfies the Stokes equations, the velocity and
pressure can be represented as layer potentials. Given the interfacial
boundary conditions~\eqref{eqn:jump}, the fluid velocity is
\begin{align}
  \uu(\xx) = \uu_\infty(\xx) + \SS[\ff_\mathrm{mem}](\xx), \quad
    \xx \in \Omega,
\end{align}
where $\SS$ is the single-layer potential
\begin{align}
  \SS[\ff](\xx) = \frac{1}{4\pi} \int_{\gamma} \left(
    -\mathbf{I} \log\rho + \frac{\rr \otimes \rr}{\rho^2} \right)
    \ff(\yy) ds_{\yy},
%  \SS[\ff](\xx) = \frac{1}{4\pi\mu} \int_{\gamma} \left(
%    -\mathbf{I} \log\rho + \frac{\rr \otimes \rr}{\rho^2} \right)
%    \ff(\yy) ds_{\yy},
\end{align}
with $\rr = \xx - \yy$ and $\rho = |\rr|$. 
Together with the inextensibility constraint and the dimensionless boundary condition
\begin{align}
  \label{eqn:vesicleFlux}
  \uu - \dot{\xx} = - \beta (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
  \xx \in \gamma,
\end{align}
%
%Semipermeability is introduced by modifying the vesicle velocity from
%the standard no-slip condition $\dot{\xx} = \uu(\xx)$. Instead,
%the permeating water flux through the lipid bilayer membrane is proportional to the
%membrane traction~\cite{yao-mor2017}. That is, 
%\begin{align}
%  \label{eqn:vesicleFlux}
%  \uu - \dot{\xx} = - \beta (\ff_\mathrm{mem} \cdot \nn) \nn, \qquad
%  \xx \in \gamma,
%\end{align}
%where $\beta = k_w/(R_0/\mu)$ is the dimensionless membrane permeability for water.
%
%Imposing the flux
%condition~\eqref{eqn:vesicleFlux} and the inextensibility condition, 
the vesicle membrane velocity satisfies the boundary integral equation
\begin{align}
  \label{eqn:vesVelocity}
  \dot{\xx} &= \uu_\infty(\xx) + \beta (\ff_\mathrm{mem}\cdot\nn)\nn
  + \SS [\ff_\mathrm{mem}](\xx),  \quad
  \xx_s \cdot \dot{\xx}_s = 0.
\end{align}
In confined geometries, the far field term $\uu_\infty(\xx)$ is replaced
by a double-layer potential with an unknown density defined on
$\partial\Omega$. The density function is used to satisfy the boundary
condition on $\partial\Omega$. Specifically, in the two examples of a semipermeable vesicle under strong confinement, we enforce a
no-slip boundary condition along the top and bottom of the channel and a
Hagen–Poiseuille flow at the inlet and outlet---this boundary condition
has been used in similar vesicle setups~\cite{qua-bir2014,
rah-vee-bir2010, lu-rah-zor2017}.

The value of $\beta$ can be estimated by first
converting the apparent permeability of a 
bilayer~\cite{OlbrichRawiczNeedhamEtAl2000_BJ} to the hydraulic
conductivity $k_w$ using the conversion
in~\cite{FettiplaceHaydon1980_PhysRev}, and then scaling $k_w$ to $R_0/\mu$. We found that for most lipid bilayer membranes, $10^{-14}\le
k_w\le 10^{-12}$ m$^2$s/kg, thus the range of $\beta$ corresponding to the native membrane permeability for water is $10^{-11}\le
\beta\le 10^{-9}$. 
%
Under strong confinement, a large value of $\beta$ is needed in
our simulations to keep the membrane tension below the threshold value
for membrane poration $\sim 10^{-3}$ N/m. Such large value of $\beta$
may pertain to red blood cell membranes with aquaporin proteins.

@@

\section{Hydrodynamics of a semipermeable vesicle in free space\label{sec:free_space}}
To highlight the effects of membrane permeability to water, we consider
a single semipermeable vesicle, with (dimensionless) permeability
coefficient $\beta>0$, in familiar configurations: In free space we
place a semipermeable vesicle in a quiescent flow, a planar shear flow,
and a Poiseuille flow. For each example, we fix the vesicle length and
examine the enclosed water content as a dynamic consequence of water
flow, vesicle shape deformation, and membrane tension distribution.
%
Under these flows, our simulations show
that the steady state of an impermeable vesicle is different from that of a semipermeable vesicle, which depends only on the strength of the external flow and is insensitive to permeability $\beta$ (as long as $\beta>0$). We find that  the time in the dynamic evolution towards equilibrium is scaled by $\beta^{-1}$: the smaller $\beta$ is the longer it takes to reach the steady state.

@@

\section{A semipermeable vesicle under strong confinement\label{sec:confinement}}
Here we consider a semipermeable vesicle under strong confinement: a
long closely-fit channel and a contracting channel. In a narrow
microfluidic channel, a large pressure jump is often needed to push the
vesicle through a closely-fit channel~\cite{abk-fai-sto2006}.  Our
simulations show that such a configuration can lead to an amplification
of water permeation at a time scale shorter than a few minutes. In
addition, we find that a large value of $\beta$ is needed to keep the
membrane tension below the threshold value for membrane poration. Such
high permeability for water may be regarded as an indication that the
lipid bilayer membrane is porated under strong confinement, and our
model vesicle is for a porated vesicle within the Helfrich free energy
framework.  As in the previous examples, we fix the vesicle length and
examine the enclosed water content as a dynamic consequence of water
flow, vesicle shape deformation, and membrane tension distribution.

@@

\acknowledgments
We thank Howard A.~Stone, Michael J.~Shelley, Petia M.~Vlahovska,
Chaoqui Misbah, Manouk Abkarian, Sangwoo Shin, and Shravan
K.~Veerapaneni for discussions. B.Q.~acknowledges support from the
Simons Foundation, Mathematics and Physical Sciences-Collaboration
Grants for Mathematicians, Award Number 527139.  Y.-N.Y.~acknowledges
support from NSF (DMS 1614863, DMS 195160) and Flatiron Institute, part
of Simons Foundation.
